method

### 2021-08-27 06_Paper/ER-ED/method.Rmd
added text

"We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012]

@@

The study consisted of two sessions, one week apart. 
Both sessions took place in a shielded cabin with constant lighting. 
Before each session, participants received information about the respective experimental procedure and signed informed consent. 
At the beginning of the first session participants filled out a demographic questionnaire. 
Afterwards the completed an n-Back task

@@

stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","neutral.xlsx")), range = cell_rows(1:21))

```
## 2.4. Stimuli

>>>>

The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED. 
"We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012]. 
A complete list of all measures assessed in the study can be found at the OSF (https://osf.io/vnj8x/) and GitHub (github.com/ChScheffel/COG-ER-ED). <!-- Attention! OSF is still private -->
All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.

@@

The study consisted of two sessions, one week apart. 
Both sessions took place in a shielded cabin with constant lighting. 
Before each session, participants received information about the respective experimental procedure and signed informed consent. 
At the beginning of the first session participants filled out a demographic questionnaire. 
Afterwards the completed an n-Back task with the levels one to four.

@@

stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","neutral.xlsx")), range = cell_rows(1:21))
```
## 2.4. Stimuli
